---
title: "Interim Streamflow Duration Assessment Method for the Arid West"
subtitle: "Classification Report"
author: "developed by the Southern California Coastal Water Research Project for the Environmental Protection Agency"
date: "Report generated on: `r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
params:
  a: NA
  b: NA
  c: NA
  d: NA
  e: NA
  f: NA
  g: NA
  h: NA
  i: NA
  j: NA
  k: NA
  l: NA
  m: NA
  n: NA
  o: NA
  p: NA
  r: NA
  s: NA
  t: NA
  u: NA
  v: NA
  w: NA
  x: NA
  aa: NA
  ab: NA
  ac: NA
  ad: NA
  ae: NA
  af: NA
  ag: NA
  ah: NA
  ai: NA
  aj: NA
  ak: NA
  al: NA
  am: NA
  an: NA
  ao: NA
  ap: NA
  aq: NA
  ar: NA
  as: NA
  at: NA
  av: NA
  ba: NA
  bb: NA
  bc: NA
  bd: NA
  be: NA
  bf: NA
  bg: NA
  rf: NA
  
---

```{r, setup, include=FALSE}

# Removing all code from appearing in the final knit document.
knitr::opts_chunk$set(echo = FALSE)

# Removing all "#" from appearing in the final knit document.
knitr::opts_chunk$set(comment = NA)

```

## General Site Information

Project name or number:
```{r}
# Adding cat() to all of the outputs to remove the [1] that would otherwise print immediately before them.
cat(params$a)
```

Site code or identifier:
```{r}
cat(params$c)
```

Assessor(s):
```{r}
cat(params$b)
```

Waterway name:
```{r}
cat(params$d)
```

Visit date:
```{r}
cat(params$e)
```

## Classification:

```{r}
cat(params[["rf"]])
```

***

Weather conditions:
```{r}
cat(params$j)
```

Location:
```{r}
cat(paste0(params$g," N, ", params$h, " E"))
```

Datum:
```{r}
cat(params$i)
```

Surrounding land use within 100 m:
```{r}
cat(params$l)
```

Reach boundaries:
```{r}
cat(params$f)
```

Mean channel width (m):
```{r}
cat(params$p)
```

Reach length (m):
```{r}
cat(params$r)
```

Disturbed site/difficult situation:
```{r}
cat(params$k)
```

Observed hydrology:

Percent of reach with surface flow:
```{r}
cat(params$m)
```

Percent of reach with surface and sub-surface flows:
```{r}
cat(params$n)
```

Number of isolated pools:
```{r}
cat(params$o)
```

## Site photos

Top of reach looking downstream:
```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["v"]])
```

Middle of reach looking upstream:
```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["u"]])
```

Middle of reach looking downstream:
```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["t"]])
```

Bottom of reach looking upstream:
```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["s"]])
```

## Site Sketch

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["w"]])
```

## Hydrophytic Vegetation

Number of hydrophytes reported:
```{r}
cat(params$av)
```

```{r, out.width='25%', fig.align='center', fig.cap=params$ab}
knitr::include_graphics(params[["aa"]])
```

```{r, out.width='25%', fig.align='center', fig.cap=params$ad}
knitr::include_graphics(params[["ac"]])
```

```{r, out.width='25%', fig.align='center', fig.cap=params$af}
knitr::include_graphics(params[["ae"]])
```

```{r, out.width='25%', fig.align='center', fig.cap=params$ah}
knitr::include_graphics(params[["ag"]])
```

General notes about hydrophytic vegetation:
```{r}
cat(params$bc)
```

## Algae cover

Cover of live or dead algal mats in streambed:
```{r}
cat(params$ao)
```

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["ap"]])
```

General notes about algae:
```{r}
cat(params$bb)
```

## Aquatic invertebrates

Number of individuals observed:
```{r}
cat(params$ai)
```

Are mayflies, stoneflies, or caddisflies present?
```{r}
cat(params$aj)
```

Invertebrate taxa observed:
```{r}
cat(params$ak)
```

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["al"]])
```

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["am"]])
```

General notes about aquatic invertebrates:
```{r}
cat(params$an)
```

## Single indicators

Fish observed:
```{r}
cat(params$aq)
```

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["ar"]])
```

General notes about fish:
```{r}
cat(params$bd)
```

Aquatic amphibians observed:
```{r}
cat(params$as)
```

Aquatic snakes observed:
```{r}
cat(params$at)
```

## Other indicators
```{r}
cat(params$bf)
```

## Additional photo(s)

```{r, out.width='25%', fig.align='center', fig.cap = params$be}
knitr::include_graphics(params[["ba"]])
```

## Additional notes about the assessment
```{r}
cat(params$bg)
```

***