---
title: "Field Form for Arid West Streamflow Duration Assessment Method"
author: "developed by the Southern California Coastal Water Research Project"
date: "Report generated on: `r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
params:
  a: NA
  b: NA
  c: NA
  d: NA
  e: NA
  f: NA
  g: NA
  h: NA
  i: NA
  j: NA
  k: NA
  l: NA
  m: NA
  n: NA
  o: NA
  p: NA
  q: NA
  r: NA
  s: NA
  t: NA
  u: NA
  v: NA
  w: NA
  x: NA
  aa: NA
  ac: NA
  ae: NA
  ag: NA
  ai: NA
  aj: NA
  ak: NA
  al: NA
  am: NA
  an: NA
  ao: NA
  ap: NA
  aq: NA
  ar: NA
  as: NA
  at: NA
  av: NA
  ba: NA
  
---

```{r, setup, include=FALSE}

# Removing all code from appearing in the final knit document.
knitr::opts_chunk$set(echo = FALSE)

```

### General Site Information

Project name or number:
```{r}
params$a
```

Assessor(s):
```{r}
params$b
```

Site address:
```{r}
params$c
```

Waterway name:
```{r}
params$d
```

Assessment date:
```{r}
params$e
```

**Determination:**
```{r}
# INSERT RF MODEL OUTPUT HERE.
```

***
Reach boundaries:
```{r}
params$f
```

Latitude, Longitude at downstream end (d.ddddd N, d.ddddd E):
```{r}
params$g 
params$h
```

Datum:
```{r}
params$i
```

Weather:
```{r}
params$j
```

Disturbed site/difficult situation:
```{r}
params$k
```

Surrounding land use:
```{r}
params$l
```

Percent of reach with surface flows:
```{r}
params$m
```

Percent of reach with surface and sub-surface flows:
```{r}
params$n
```

Number of isolated pools:
```{r}
params$o
```

Average bankwidth (m):
```{r}
params$p
```

Recommended reach length (m):
```{r}
params$q
```

Actual reach length (m):
```{r}
params$r
```

### Site photos

Bottom looking up:
```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["s"]])
```

Middle looking down:
```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["t"]])
```

Middle looking up:
```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["u"]])
```

Top looking down:
```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["v"]])
```

Site sketch:
```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["w"]])
```

### Hydrophytes

Checklist:
```{r}
params$x
```

Number of hydrophytes reported:
```{r}
params$av
```

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["aa"]])
```

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["ac"]])
```

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["ae"]])
```

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["ag"]])
```

### Aquatic invertebrates

Abundance:
```{r}
params$ai
```

EPT present:
```{r}
params$aj
```

Invertebrate taxa observed:
```{r}
params$ak
```

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["al"]])
```

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["am"]])
```

Notes about aquatic invertebrates:
```{r}
params$an
```

### Algae cover

Live or dead algae:
```{r}
params$ao
```

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["ap"]])
```

### Vertebrates

Fish observed:
```{r}
params$aq
```

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["ar"]])
```

Aquatic amphibians observed:
```{r}
params$as
```

Aquatic snakes observed:
```{r}
params$at
```

### Additional photo(s)

```{r, out.width='25%', fig.align='center'}
knitr::include_graphics(params[["ba"]])
```

***