---
title: "Field form for the Arid West Streamflow Duration Assessment Method"
author: "Southern California Coastal Water Research Project"
date: "Report generated on:`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
params:
  a: NA
  b: NA
  c: NA
  d: NA
  e: NA
  f: NA
  g: NA
  h: NA
  i: NA
  j: NA
  k: NA
  l: NA
  m: NA
  n: NA
  o: NA
  p: NA
  q: NA
  r: NA
---

```{r, setup, include=FALSE}

# Removing all code from appearing in the final knit document.
knitr::opts_chunk$set(echo = FALSE)

```

### General Site Information

Project name or number:
```{r}
params$a
```

Assessor(s):
```{r}
params$b
```

Site address:
```{r}
params$c
```

Waterway name:
```{r}
params$d
```

Assessment date:
```{r}
params$e
```

**Determination:**
```{r}
# INSERT RF MODEL OUTPUT HERE.
```

***
Reach boundaries:
```{r}
params$f
```

Latitude, Longitude at downstream end (d.ddddd N, d.ddddd E):
```{r}
params$g 
params$h
```

Datum:
```{r}
params$i
```

Weather:
```{r}
params$j
```

Disturbed site/difficult situation:
```{r}
params$k
```

Surrounding land use:
```{r}
params$l
```

Percent of reach with surface flows:
```{r}
params$m
```

Percent of reach with surface and sub-surface flows:
```{r}
params$n
```

Number of isolated pools:
```{r}
params$o
```

Average bankwidth (m):
```{r}
params$p
```

Recommended reach length (m):
```{r}
params$q
```

Actual reach length (m):
```{r}
params$r
```
